---
date: "`r paste('Received on', format(ymd(filter(dates_received, country == i) %>% pull(date)), '%d %B %Y'))`"
output: html_document
---

---
title: `r paste(i, " - FM DATA REPORTED")`
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(dpi = 72, fig.asp = 0.75, fig.width = 12.638, fig.retina = 1, fig.align = "left")
theme_set(theme_bw()) # set simple theme for charts
theme_update(text = element_text(size = 15))
options(knitr.kable.NA = '')
```

# {.tabset .tabset-pills}

## Aquaculture {.tabset}

### Received

```{r aquaculture_received_fig, echo = FALSE, message = FALSE, warning = FALSE, results='asis'}

if (nrow(filter(filtered_received, `Working domain` == "Aquaculture")) > 0) {
 
  rainbow_chart(data = filter(filtered_received, `Working domain` == "Aquaculture"), country = i, sector =
  "Aquaculture", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r aquaculture_received_table, echo = FALSE, message = FALSE, warning = FALSE, results='asis'}

if (nrow(filter(filtered_received, `Working domain` == "Aquaculture")) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` == "Aquaculture")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r aquaculture_sent_fig, echo = FALSE, message = FALSE, warning = FALSE, results='asis'}

if (nrow(filter(filtered_sent, `Working domain` == "Aquaculture")) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` == "Aquaculture"), country = i, sector = "Aquaculture",
    year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r aquaculture_sent_table, echo = FALSE, message = FALSE, warning = FALSE, results='asis'}

if (nrow(filter(filtered_sent, `Working domain` == "Aquaculture")) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` == "Aquaculture")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Inland Waters Fishing {.tabset}

### Received

```{r inland_received_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Inland Waters Fishing")) > 0) {
 
  rainbow_chart(data = filter(filtered_received, `Working domain` == "Inland Waters Fishing"), country = i, sector = "Inland Waters Fishing", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r inland_received_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Inland Waters Fishing")) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` == "Inland Waters Fishing")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r inland_sent_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Inland Waters Fishing")) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` == "Inland Waters Fishing"), country = i, sector = "Inland Waters Fishing", year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r inland_sent_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Inland Waters Fishing")) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` == "Inland Waters Fishing")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Marine Coastal Fishing {.tabset}

### Received

```{r coastal_received_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Marine Coastal Fishing")) > 0) {
 
  rainbow_chart(data = filter(filtered_received, `Working domain` == "Marine Coastal Fishing"), country = i, sector = "Marine Coastal Fishing", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r coastal_received_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Marine Coastal Fishing")) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` == "Marine Coastal Fishing")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r coastal_sent_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Marine Coastal Fishing")) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` == "Marine Coastal Fishing"), country = i, sector = "Marine Coastal Fishing", year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r coastal_sent_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Marine Coastal Fishing")) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` == "Marine Coastal Fishing")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Marine Deep-Sea Fishing  {.tabset}

### Received

```{r deepsea_received_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Marine Deep-Sea Fishing")) > 0) {
 
  rainbow_chart(data = filter(filtered_received, `Working domain` == "Marine Deep-Sea Fishing"), country = i, sector = "Marine Deep-Sea Fishing", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r deepsea_received_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Marine Deep-Sea Fishing")) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` == "Marine Deep-Sea Fishing")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r deepsea_sent_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Marine Deep-Sea Fishing")) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` == "Marine Deep-Sea Fishing"), country = i, sector = "Marine Deep-Sea Fishing", year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r deepsea_sent_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Marine Deep-Sea Fishing")) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` == "Marine Deep-Sea Fishing")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Marine Fishing, nei {.tabset}

### Received

```{r fishingnei_received_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Marine Fishing, nei")) > 0) {
 
  rainbow_chart(data = filter(filtered_received, `Working domain` == "Marine Fishing, nei"), country = i, sector = "Marine Fishing, nei", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r fishingnei_received_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Marine Fishing, nei")) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` == "Marine Fishing, nei")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r fishingnei_sent_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Marine Fishing, nei")) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` == "Marine Fishing, nei"), country = i, sector = "Marine Fishing, nei", year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r fishingnei_sent_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Marine Fishing, nei")) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` == "Marine Fishing, nei")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Marine Fishing (combined) {.tabset}

### Received

```{r marinefishing_received_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` %in% c("Marine Coastal Fishing", "Marine Deep-Sea Fishing", "Marine Fishing, nei"))) > 0) {
 
  rainbow_chart(data = filter(filtered_received, `Working domain` %in% c("Marine Coastal Fishing", "Marine Deep-Sea Fishing", "Marine Fishing, nei")), country = i, sector = "Marine Fishing (combined)", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r marinefishing_received_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` %in% c("Marine Coastal Fishing", "Marine Deep-Sea Fishing", "Marine Fishing, nei"))) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` %in% c("Marine Coastal Fishing", "Marine Deep-Sea Fishing", "Marine Fishing, nei"))) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r marinefishing_sent_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` %in% c("Marine Coastal Fishing", "Marine Deep-Sea Fishing", "Marine Fishing, nei"))) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` %in% c("Marine Coastal Fishing", "Marine Deep-Sea Fishing", "Marine Fishing, nei")), country = i, sector = "Marine Fishing (combined)", year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r marinefishing_sent_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` %in% c("Marine Coastal Fishing", "Marine Deep-Sea Fishing", "Marine Fishing, nei"))) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` %in% c("Marine Coastal Fishing", "Marine Deep-Sea Fishing", "Marine Fishing, nei"))) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Subsistence {.tabset}

### Received

```{r subsistence_received_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Subsistence")) > 0) {
 
  rainbow_chart(data = filter(filtered_received, `Working domain` == "Subsistence"), country = i, sector = "Subsistence", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r subsistence_received_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Subsistence")) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` == "Subsistence")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r subsistence_sent_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Subsistence")) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` == "Subsistence"), country = i, sector = "Subsistence", year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r subsistence_sent_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Subsistence")) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` == "Subsistence")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Processing {.tabset}

### Received

```{r processing_received_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Processing")) > 0) {

  rainbow_chart(data = filter(filtered_received, `Working domain` == "Processing"), country = i, sector = "Processing", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r processing_received_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Processing")) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` == "Processing")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r processing_sent_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Processing")) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` == "Processing"), country = i, sector = "Processing", year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r processing_sent_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Processing")) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` == "Processing")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Unspecified {.tabset}

### Received

```{r unspecified_received_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Unspecified")) > 0) {
 
  rainbow_chart(data = filter(filtered_received, `Working domain` == "Unspecified"), country = i, sector = "Unspecified", year_start = start_year, year_end = end_year, title = "Data reported by the country")
  
} else {print("No data.")}

```

---

```{r unspecified_received_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_received, `Working domain` == "Unspecified")) > 0) {
  
  knitr::kable(filter(filtered_received, `Working domain` == "Unspecified")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

### Sent

```{r unspecified_sent_fig, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Unspecified")) > 0) {
 
  rainbow_chart(data = filter(filtered_sent, `Working domain` == "Unspecified"), country = i, sector = "Unspecified", year_start = start_year, year_end = end_year, title = "Data sent to the country")
  
} else {print("No data.")}

```

---

```{r unspecified_sent_table, echo = FALSE, message = FALSE, warning = FALSE}

if (nrow(filter(filtered_sent, `Working domain` == "Unspecified")) > 0) {
  
  knitr::kable(filter(filtered_sent, `Working domain` == "Unspecified")) %>%
    kable_styling(full_width = F)
  
} else {print("No data.")}

```

## Comparison {.tabset .active}

### Comparison table

```{r comparison_table, echo = FALSE, results = 'asis', message = FALSE}

# Create comparison table between sent and received data

comparison_output <- suppressMessages(
      compare_df(
      df_new = filtered_received, 
      df_old = filtered_sent, 
      group_col = c("Country", "Working domain", "Working Status", "Sex", "Year"),
      stop_on_error = FALSE
      )
    )

# Output HTML table

suppressMessages(
    create_output_table(comparison_output,
                      output_type = "html",
                      limit = 3000)
  )

```